\documentclass[a4paper,10pt]{article}

%---------------------------%
%   PACKAGES & CONFIG
%---------------------------%
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

% Section formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-4pt}]

%---------------------------%
%   HEADER
%---------------------------%
\begin{document}

\begin{center}
    {\LARGE \textbf{Dylan Alexander}} \\
    \vspace{3pt}
    \faPhone\ (770) 343-1748 \quad
    \faEnvelope\ \href{mailto:dylanjalexander2@gmail.com}{dylanjalexander2@gmail.com} \quad
    \faMapMarker*\ Atlanta, GA \\
    \vspace{3pt}
    \href{https://linkedin.com}{LinkedIn} \quad | \quad
    \href{https://github.com}{GitHub}
\end{center}

%---------------------------%
%   PROFILE
%---------------------------%
\section*{Profile}
Senior Machine Learning Engineer specializing in productizing researcher prototypes into scalable, GPU-accelerated microservices. Recognized for delivering business-aligned AI solutions by uniting researchers with product management.

%---------------------------%
%   EXPERIENCE
%---------------------------%
\section*{Professional Experience}

\textbf{NiCE (NASDAQ: NICE)} \hfill \textit{Atlanta, GA} \\
\textit{Senior R\&D Software Engineer} \hfill Apr 2022 -- Present \\
\textit{Technologies: Python, gRPC, Docker, SentenceTransformers, FAISS, AWS Bedrock, AWS ECS, S3}
\begin{itemize}[leftmargin=*]
    \item Lead development of “Topic Detection” API, a Python microservice embedded across the CXOne Platform, serving analytics to 1000+ enterprise clients and processing millions of conversations daily.
    \item Productized NLP researcher POCs into containerized, GPU-optimized applications that scaled into production-ready services, improving throughput by orders of magnitude.
    \item Architected ML workflows bridging product and research teams, improving topic detection accuracy and driving adoption of advanced API features.
    \item Standardized research-to-production pipelines via a gRPC Python template repo, reducing prototype-to-deployment from months to weeks.
    \item Benchmarked performance at production scale with sandbox pipelines monitoring latency, throughput, and GPU/CPU utilization.
\end{itemize}

\vspace{4pt}
\textbf{Carter + Clark} \hfill \textit{Duluth, GA} \\
\textit{R\&D Software Engineer} \hfill Mar 2021 -- Apr 2022 \\
\textit{Technologies: C\#, .NET Framework, AutoCAD .NET API, Jenkins}
\begin{itemize}[leftmargin=*]
    \item Engineered \textbf{DynamiCAD}, an in-house permit drawing automation tool adopted company-wide.
    \item Reduced manual drafting time by \textbf{~78\%} by automating geometric computation algorithms for house plan generation.
    \item Designed advanced spatial algorithms for rotation, scaling, and centering across variable lot orientations.
    \item Drove iterative development cycles, implemented CI/CD pipelines, and collaborated with drafting teams for refinement.
\end{itemize}

\vspace{4pt}
\textbf{ManDeo Consultancy} \hfill \textit{Atlanta, GA} \\
\textit{Full Stack Developer} \hfill Jun 2020 -- Mar 2021 \\
\textit{Technologies: LAMP Stack, JavaScript, PHP, MySQL, Square API}
\begin{itemize}[leftmargin=*]
    \item Designed and launched 10+ client-facing web apps including Scofflaw Brewing’s e-commerce site with Square API integration.
\end{itemize}

\vspace{4pt}
\textbf{173rd Airborne Brigade, U.S. Army} \hfill \textit{Vicenza, Italy} \\
\textit{Geospatial Engineer} \hfill Jun 2018 -- Jun 2020 \\
\textit{Technologies: Python, GeoPandas, ArcGIS, Satellite Imagery}
\begin{itemize}[leftmargin=*]
    \item Developed data pipelines for cleaning and analyzing geospatial datasets to detect terrain and troop movement.
    \item Produced mission-critical cartographic products supporting NATO/EUCOM operational planning.
\end{itemize}

%---------------------------%
%   EDUCATION
%---------------------------%
\section*{Education \& Certifications}
\textbf{University of Georgia} \hfill \textit{Athens, GA} \\
Professional MBA, Leadership

\textbf{Kennesaw State University} \hfill \textit{Kennesaw, GA} \\
Bachelor of Science, Computer Science (AI \& ML)

\vspace{4pt}
AWS Cloud Practitioner (Mar 2021) \quad | \quad GEOINT Professional (Nov 2020) \quad | \quad Security Clearance: TS/SCI (Jan 2019)

\end{document}
